diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2019-11-18 jss-article-rnw-diffEnrich/article.Rnw
Started Step 1 instruction in Rnw

>>>>

The \code{get_kegg} function accesses the KEGG REST API and downloads the data
sets required to perform downstream analysis. This function takes two arguments.
The first, 'species' is required. Currently, diffEnrich supports three species,
and the argument is a character string using the KEGG code: Homo sapiens
(human), use 'hsa'; Mus musculus (mouse), use 'mmu'; and Rattus norvegicus
(rat), use 'rno'. The second, 'path' is also passed as a character string, and
is the path of the directory in which the user would like to write the data sets
downloaded from the KEGG REST API. If the user does not provide a path, the data
sets will be automatically written to the current working directory using the
\code{here::here()} (\cite{kirill:2017}) functionality. These data sets will be
tab delimited files with a name describing the data, and for reproducibility,
the date they were generated and the version of KEGG when the API was accessed.
In addition to these flat files, \code{get_kegg} will also create a named list
in R with the three relevant KEGG data sets. The names of this list will
describe the data set, and are described in Table 1.
